On Secure Delegation of SampBQP with a Classical Client

### 2019-11-28 preliminaries.tex

Here is a theorem taken from \cite{Brandão2017}.
\begin{theorem}
	\label{deFinetti}
	Let $\rho^{A_1\ldots A_k}$ be a permutation-invariant state. Then for every $0\leq l\leq k$ there is a measure $\nu$ on $D(A)$ such that
	$$\max_{\Lambda_2,\ldots,\Lambda_l\in\mathcal{M}}\norm{(id\otimes\Lambda_2\otimes\ldots\otimes\Lambda_l)\left(\rho^{A_1\ldots A_l}-\int \nu(d\sigma)\sigma^{\otimes l}\right)}_1\leq\sqrt{\frac{2l^2\ln\abs{A}}{k-l}}$$
\end{theorem}

\Ethan{Explain the terminologies. Also check do something about the integral vs weighted sum}

>>>>

Here is a theorem taken from \cite{Brandão2017}.
\begin{theorem}
	\label{deFinetti}
	Let $\rho^{A_1\ldots A_k}$ be a permutation-invariant state. Then for every $0\leq l\leq k$ there exists states $\set{\rho_i}$ and $\set{p_i}\subset\bbR$ such that
	$$\max_{\Lambda_1,\ldots,\Lambda_l}\norm{(\Lambda_1\otimes\ldots\otimes\Lambda_l)\left(\rho^{A_1\ldots A_l}-\sum_ip_i\rho_i^{A_1}\otimes\ldots\otimes\rho_i^{A_l}\right)}_1\leq\sqrt{\frac{2l^2\ln\abs{A}}{k-l}}$$
\end{theorem}
